Mahotas: Open source software for scriptable computer vision

### 2012-07-16 paper.tex
MIN A note about ml libraries

@@

It has been available in the Python Package Index since April~2010 and has been
downloaded over 20,000~times. This does not include any downloads from other
sources.

>>>>

Mahotas does not include machine learning related functionality, such as
$k$-means clustering or any classification. This is the result of an explicit
design decision. Specialised machine learning packages for Python (e.g.,
milk\footnote{http://github.com/luispedro/milk},
scikit-learn\footnote{http://}) already exist. A good classification system can
benefit both computer vision users and others. As these projects all use Numpy
arrays as their datatypes, it is easy to use functionality from the different
project seamlessly (including without any extra copying of data).

@@

It has been available in the Python Package Index since April~2010 and has been
downloaded over 20,000~times\footnote{This does not include any downloads from
other sources.}.
